مفاهیم اولیه بلاک چین

### 2024-07-30 papers/main.tex
comment future concepts

\subsubsection{مفهوم \lr{Gas Limit}}

@@

\subsection{\lr{Transaction fee}}

@@

\subsection{\lr{Block Gas Limit}}

\subsection{\lr{Base Fee}}

\begin{LTR}
    \begin{lstlisting}

   Deploying 'Counter'
   -------------------
   > transaction hash:    0x5f3ef7d437030295573fa20561880eb1a238ac9179d28da1892b98a4accce11b
   > Blocks: 0            Seconds: 0
   > contract address:    0xbE89bA3ea69CDC37Fb819E27291D86dD26CAFD41
   > block number:        1
   > block timestamp:     1722330386
   > account:             0x821F2dCfC492681b2260B9C29e4982155b0ef885
   > balance:             99.999174863125
   > gas used:            244485 (0x3bb05)
   > gas price:           3.375 gwei
   > value sent:          0 ETH
   > total cost:          0.000825136875 ETH

   > Saving artifacts
   -------------------------------------
   > Total cost:      0.000825136875 ETH
    \end{lstlisting}
\end{LTR}

@@

\subsection{\lr{Priority Fee}}

\subsection{\lr{Max Fee}}

\subsection{\lr{Contract}}

\subsection{\lr{EVM}}

@@

\subsection{\lr{Transactions (Read \& Write)}}

>>>>

\subsection{مفهوم \lr{Gas Limit}}

@@

\subsection{مفهوم \lr{Transaction fee}}

@@

% \subsection{\lr{Block Gas Limit}}

% \subsection{\lr{Base Fee}}

% \begin{LTR}
%     \begin{lstlisting}

%    Deploying 'Counter'
%    -------------------
%    > transaction hash:    0x5f3ef7d437030295573fa20561880eb1a238ac9179d28da1892b98a4accce11b
%    > Blocks: 0            Seconds: 0
%    > contract address:    0xbE89bA3ea69CDC37Fb819E27291D86dD26CAFD41
%    > block number:        1
%    > block timestamp:     1722330386
%    > account:             0x821F2dCfC492681b2260B9C29e4982155b0ef885
%    > balance:             99.999174863125
%    > gas used:            244485 (0x3bb05)
%    > gas price:           3.375 gwei
%    > value sent:          0 ETH
%    > total cost:          0.000825136875 ETH

%    > Saving artifacts
%    -------------------------------------
%    > Total cost:      0.000825136875 ETH
%     \end{lstlisting}
% \end{LTR}

@@

% \subsection{\lr{Priority Fee}}

% \subsection{\lr{Max Fee}}

% \subsection{\lr{Contract}}

% \subsection{\lr{EVM}}

@@

% \subsection{\lr{Transactions (Read \& Write)}}
